Declarative runtime reconfiguration of pulverised distributed systems \thanks{Identify applicable funding agency here. If none, delete this.}

### 2023-05-10 paper-2023-acsos-pulverization.tex
More related?

\meta{
%
%\subsection{Approaches to Deployment Independence}
%\label{s:rw:deployment-independence}
%
%\meta{TODO: add works on deployment independence, e.g., osmotic~\citep{DBLP:journals/computer/VillariFDRJR19}, BIP~\citep{lekidis2015bip-wsn,bastarrica2001optimization-techniques-deployment-components-bip}}
%
We highlight a number of representatieve research efforts on deployment and automatic reconfiguration of systems.
%
%For instance, 
\emph{Osmotic computing}~\cite{DBLP:journals/computer/VillariFDRJR19} is an approach to opportunistic deployment of microservices on the edge-fog-cloud platform.
An osmotic platform aims to reach and maintain an ``osmotic equilibrium'' 
between infrastructural and application requirements
by automatically migrating microservices to deployment locations.
%
However, the approach mainly targets centrally orchestrated systems.
%
Other approaches leverage component-based, architectural descriptions to decouple application logic and deployment.
%
For instance, \emph{DR-BIP (Dynamically Reconfigurable - Behaviour Interaction Priority model)}~\cite{,Ballouli18dr-bip}
and \emph{DReAM (Dynamically Reconfigurable Architectural Modelling)}~\cite{denicola2020dream-dynamic-reconfig-arch-modelling}
use \emph{components} (capturing behaviour), \emph{connectors} (capturing interaction between components' \emph{ports}), 
\emph{maps} (logical topologies),
and \emph{deployments} (associating components to map locations),
overall organised in \emph{motifs} (dynamic architectural configurations),
to model and analyse dynamic architectures.
%

>>>>

A related approach is also provided by the so-called \emph{multi-tier programming} paradigm~\cite{DBLP:journals/csur/WeisenburgerWS20},
 whereby the code for multiple tiers (e.g., client and server tiers; or view, business logic, and data tiers) is specified in a single codebase,
 from which the code of each individual tier is compiled.

\meta{
MuScADeL (Multi-Scale Autonomic Deployment Language)~\cite{DBLP:conf/compsac/BoujbelRLTAL14/muscadel}

ADSL (AWaRE DSL)~\cite{DBLP:conf/aswec/ChhetriLUVKNR18/adsl} % and see corresp RW

%
%\subsection{Approaches to Deployment Independence}
%\label{s:rw:deployment-independence}
%
%\meta{TODO: add works on deployment independence, e.g., osmotic~\citep{DBLP:journals/computer/VillariFDRJR19}, BIP~\citep{lekidis2015bip-wsn,bastarrica2001optimization-techniques-deployment-components-bip}}
%
We highlight a number of representatieve research efforts on deployment and automatic reconfiguration of systems.
%
%For instance, 
\emph{Osmotic computing}~\cite{DBLP:journals/computer/VillariFDRJR19} is an approach to opportunistic deployment of microservices on the edge-fog-cloud platform.
An osmotic platform aims to reach and maintain an ``osmotic equilibrium'' 
between infrastructural and application requirements
by automatically migrating microservices to deployment locations.
%
However, the approach mainly targets centrally orchestrated systems.
%
Other approaches leverage component-based, architectural descriptions to decouple application logic and deployment.
%
For instance, \emph{DR-BIP (Dynamically Reconfigurable - Behaviour Interaction Priority model)}~\cite{,Ballouli18dr-bip}
and \emph{DReAM (Dynamically Reconfigurable Architectural Modelling)}~\cite{denicola2020dream-dynamic-reconfig-arch-modelling}
use \emph{components} (capturing behaviour), \emph{connectors} (capturing interaction between components' \emph{ports}), 
\emph{maps} (logical topologies),
and \emph{deployments} (associating components to map locations),
overall organised in \emph{motifs} (dynamic architectural configurations),
to model and analyse dynamic architectures.
%
